News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-05 rupnik2015.tex
changes

\paragraph{Remark}
 The technique is related to  Generalization of Canonical Correlation Analysis (GCCA) by Carroll \citeyear{Carroll}, where an unknown group configuration variable is defined and the objective is to maximize the sum of squared correlation between the group variable and the others. The problem can be reformulated as an eigenvalue problem. The difference lies in the fact that we set the unknown group configuration variable as the hub language, which simplifies the solution. The complexity of our method is $O(k^3)$, where $k$ is the reduced dimension from the LSI preprocessing step, whereas solving the GCCA method scales as $O(s^3)$, where $s$ is the number of samples (see \cite{gifi}). Another issue with GCCA is that it cannot be directly applied to the case of missing documents.

>>>>

\paragraph{Remark.} The technique is related to  Generalization of Canonical Correlation Analysis (GCCA) by Carroll \citeyear{Carroll}, where an unknown group configuration variable is defined and the objective is to maximize the sum of squared correlation between the group variable and the others. The problem can be reformulated as an eigenvalue problem. The difference lies in the fact that we set the unknown group configuration variable as the hub language, which simplifies the solution. The complexity of our method is $O(k^3)$, where $k$ is the reduced dimension from the LSI preprocessing step, whereas solving the GCCA method scales as $O(s^3)$, where $s$ is the number of samples (see \cite{gifi}). Another issue with GCCA is that it cannot be directly applied to the case of missing documents.
